---
title: "Preparing datasets" 
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
---

# Load libs 

```{r}
if (!require(pacman)) install.packages("pacman")

pacman::p_load(here, # reproducibility
               # wrangling 
               tidyverse, 
               tools, 
               jtools, 
               # data visualization 
               hrbrthemes,
               viridis, 
               ggstance, 
               patchwork,
               gridExtra,
               ggrepel)

source(here("functions", "utils.R"))
```

# Import data 

```{r}
# Get the file names 
file_names <- list.files(here("data"))[str_detect(list.files(here("data")), "2021_")]
```

```{r}
# Import the csv files; Remove the first two rows                                         
## Immigrants
immigrants_df <- read_csv_custom(1)

## Omnibus 
omnibus_df <- read_csv_custom(2)

## Name perceptions 
perceptions_df <- read_csv_custom(3)

## Name dataset
names_df <- read.csv(here("data", "names.csv"))
```

# Preprocess three datasets and merge them with the names dataset 

## Step 1 

Using common variables: age, gender, income, education, race, citizenship

Not using partisanship as it's not measured in `immigrants_df` (instead, vote choice for the 2020 US presidential election was measured.) The same applies to the citizenship variable. immigrants_df$Q111 (second generation or not)

```{r}
omnibus_df <- 
clean_omnibus_df(omnibus_df)

immigrants_df <- clean_immigrant_df(immigrants_df)

perceptions_df <- clean_perceptions_df(perceptions_df)
```

## Step 2 

```{r}
immigrants_all <- df2comb(immigrants_df, dataset = "immigrants")
omnibus_all <- df2comb(omnibus_df, dataset = "omnibus")
perceptions_all <- df2comb(perceptions_df, dataset = "perceptions")
```

# Export 

## Study 1,2,3 

```{r}
# Study1 
study1 <- perceptions_all %>%
  select(rid, name, first, last, w.asian, identity, race, specific.race, citizen, education, education.ord, income, income.ord, match) 

# Study2
study2 <- omnibus_all %>%
  select(rid, name, first, last, w.asian, identity, race, specific.race, citizen, education, education.ord, income, income.ord, match, res.age, res.male, res.income, res.edu, res.citizenship, res.race)

# Study3
study3 <- immigrants_all %>%
  select(rid, name, first, last, w.asian, identity, race, specific.race, citizen, education, education.ord, income, income.ord, match, res.age, res.male, res.income, res.edu, res.citizenship, res.race)

# Rename rid -> id, match -> correct 
study1 <- df_rename(study1)
study2 <- df_rename(study2)
study3 <- df_rename(study3)

# Save csv files 

# write.csv(study1, here("data_outputs", "study-1-names.csv"))
# write.csv(study2, here("data_outputs", "study-2-names.csv"))
# write.csv(study3, here("data_outputs", "study-3-names.csv"))

# Save rds files 

write_rds(study1, here("data_outputs", "study-1-names.rds"))
write_rds(study2, here("data_outputs", "study-2-names.rds"))
write_rds(study3, here("data_outputs", "study-3-names.rds"))

# Save the three datasets as an object     
save(study1, study2, study3, file = here("data_outputs", "study123.rda"))

# Save the three datasets as a joined dataframe (using full join)

study1 <- study1 %>% mutate(study = "Study1")
study2 <- study2 %>% mutate(study = "Study2")
study3 <- study3 %>% mutate(study = "Study3")

study_combined <- reduce(list(study1, study2, study3), full_join)

write_rds(study_combined, here("data_outputs", "study123.rds"))
```

## Names 

```{r}
# All 
df <- bind_rows(mutate(df2select(immigrants_all), Data = "Study 3"),
mutate(df2select(omnibus_all), Data = "Study 2"),
mutate(df2select(perceptions_all), Data = "Study 1"))

names <- df %>%
  group_by(name, first, last, w.asian, identity) %>%
  summarise(mean.correct = mean(match),
            sd.correct = sd(match))

#write.csv(names, here("data_outputs", "names.csv"))
write_rds(names, here("data_outputs", "names.rds"))
```