---
title: "Producing the three datasets" 
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

# Load libs 

```{r}
if (!require(pacman)) install.packages("pacman")

pacman::p_load(here, # reproducibility
               # wrangling 
               tidyverse, 
               tools, 
               jtools, 
               # data visualization 
               hrbrthemes,
               viridis, 
               ggstance, 
               patchwork,
               gridExtra,
               ggrepel)

source(here("functions", "utils.R"))

remotes::install_git("https://git.rud.is/hrbrmstr/hrbrthemes.git")
library(hrbrthemes)
```

# Import data 

```{r}
# Get the file names 
file_names <- list.files(here("data"))[str_detect(list.files(here("data")), "2021_")]
```

```{r}
# Import the csv files; Remove the first two rows                                         
## Immigrants
immigrants_df <- read_csv_custom(1)

## Omnibus 
omnibus_df <- read_csv_custom(2)

## Name perceptions 
perceptions_df <- read_csv_custom(3)

## Name dataset
names_df <- read.csv(here("data", "names.csv"))
```

# Preprocess three datasets and merge them with the names dataset 

## Step 1 

Using common variables: age, gender, income, education, race, citizenship

Not using partisanship as it's not measured in `immigrants_df` (instead, vote choice for the 2020 US presidential election was measured.) The same applies to the citizenship variable. immigrants_df$Q111 (second generation or not)

```{r}
omnibus_df <- 
clean_omnibus_df(omnibus_df)

immigrants_df <- clean_immigrant_df(immigrants_df)

perceptions_df <- clean_perceptions_df(perceptions_df)
```

## Step 2 

```{r}
immigrants_all <- df2comb(immigrants_df, dataset = "immigrants")
omnibus_all <- df2comb(omnibus_df, dataset = "omnibus")
perceptions_all <- df2comb(perceptions_df, dataset = "perceptions")

length(unique(immigrants_all$name))
length(unique(omnibus_all$name))
length(unique(perceptions_all$name))

immigrants_all %>%
  count(name) %>%
  summarise(mean = mean(n))

omnibus_all %>%
  count(name) %>%
  summarise(mean = mean(n))

perceptions_all %>%
  count(name) %>%
  summarise(mean = mean(n))
```

# Visualize 

## Separate 

```{r}
df2plot(immigrants_all) +
  plot_annotation(
    title = "Study 3",
    tag_levels = "A"
  )

ggsave(file = here("plots", "immigrants_name.png"), width = 12, height = 11, units = "in")

df2plot(omnibus_all) +
  plot_annotation(
    title = "Study 2",
    tag_levels = "A"
  )

ggsave(file = here("plots", "omnibus_name.png"), width = 12, height = 11, units = "in")

df2plot(perceptions_all) +
  plot_annotation(
    title = "Study 1",
    tag_levels = "A"
  )

ggsave(file = here("plots", "perceptions_name.png"), width = 12, height = 11, units = "in")
```

## Together

```{r}
pooled <- bind_rows(immigrants_all, 
                      omnibus_all, 
                      perceptions_all)

df <- bind_rows(mutate(df2summ(immigrants_all), Data = "Study 3"),
mutate(df2summ(omnibus_all), Data = "Study 2"),
mutate(df2summ(perceptions_all), Data = "Study 1"))
```

## Mini plots 

```{r}
df2plot_covariate(immigrants_all) +  plot_annotation(
    title = "Study 3",
    tag_levels = "A"
  )

ggsave(file = here("plots", "immigrants_name_covariate.png"), width = 12, height = 11, units = "in")

df2plot_covariate(omnibus_all) +  plot_annotation(
    title = "Study 2",
    tag_levels = "A"
  )

ggsave(file = here("plots", "omnibus_name_covariate.png"), width = 12, height = 11, units = "in")
```

```{r}
df2plot_all(df)

ggsave(here("plots", "all_name.png"), width = 12, height = 11, units = "in")

combined <- bind_rows(mutate(df2summ(immigrants_all), Data = "Study 3"),
mutate(df2summ(omnibus_all), Data = "Study 2"),
mutate(df2summ(perceptions_all), Data = "Study 1"),
mutate(df2summ(pooled), Data = "Pooled"))

df2plot_all(combined)

ggsave(here("plots", "all_name_pooled.png"), width = 12, height = 11, units = "in")
```