---
title: "Validate the datasets"
author: "Jae Yeon Kim"
date: "`r Sys.Date()`"
output: html_document
---

# Load packages 

```{r}
# R CRAN packages
if (!require(pacman)) install.packages("pacman")

pacman::p_load(tidyverse, here, glue, purrr, ggsci, ggthemes, patchwork, ggrepel, ggpubr, estimatr, fastDummies)

ggplot2::theme_set(ggplot2::theme_bw())

# Custom functions 
source(here("functions", "validate.r"))
source(here("functions", "utils.R"))
```

# Load files 

```{r}
load(file = here("data_outputs", "study123.rda"))
```

# Data wrangling

```{r}
study23 <- full_join(study2, study3)

study23 <- study23 %>%
    mutate(identity = recode(identity, 
                             "Black or African American" = "Black",
                             "Asian or Pacific Islander" = "AAPI",
                             "Hispanic" = "Latino"
                             ))

study123 <- full_join(study1, study2) %>% 
    full_join(study3)
```

# Race response distribution per name and racial prevalence 

```{r}
race_dummies <- study123 %>%
    select(race) %>%
    dummy_cols() %>%
    select(!race)
```

```{r}
study123_dummies <- bind_cols(study123, race_dummies)

dum_sum <- study123_dummies %>%
    group_by(identity, name) %>%
    summarize(white_pct = mean(race_White, na.rm = TRUE),
              asian_pct = mean(`race_Asian or Pacific Islander`, na.rm = TRUE),
              black_pct = mean(`race_Black or African American`),
              latino_pct = mean(race_Hispanic),
              other_pct = mean(race_Other))

# CSV
write_csv(dum_sum, here("data_outputs", "names_race_perception.csv"))

# RDS
write_rds(dum_sum, here("data_outputs", "names_race_perception.rds"))
```

# Correspondecne validation 

## Visualization

```{r}
group_group_plot <- map2_dfr(c("Black", "White", "AAPI", "Latino"), c("Black", "White", "AAPI", "Latino"), sum_last_first_names) %>%
    ggplot(aes(x = res.race, y = mean_correct, 
               ymax = mean_correct + 1.96*se_correct,
               ymin = mean_correct - 1.96*se_correct,
               label = round(mean_correct, 2))) +
    geom_pointrange() +
    facet_wrap(~`Name type`) +
    labs(#title = glue("Within group assessment: 
         #A group member assesses their own group's names"),
         x = "Respondent/Name", y = "% correct") +
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    ylim(c(0.3 , 1)) 
```

```{r}
white_other_plot <- map2_dfr(c("White", "White", "White"), c("Black", "AAPI", "Latino"), sum_last_first_names) %>%
    ggplot(aes(x = identity, y = mean_correct, 
               ymax = mean_correct + 1.96*se_correct,
               ymin = mean_correct - 1.96*se_correct, 
               label = round(mean_correct, 2))) +
    geom_pointrange() +
    facet_wrap(~`Name type`) +
    labs(#title = glue("Between group assessment: 
         #A white assesses other racial group members' names"),
         x = "Name", y = "% correct") +
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    ylim(c(0.3 , 1)) 
```

```{r}
other_white_plot <- map2_dfr(c("Black", "AAPI", "Latino"), c("White", "White", "White"), sum_last_first_names) %>%
    ggplot(aes(x = res.race, y = mean_correct, 
               ymax = mean_correct + 1.96*se_correct,
               ymin = mean_correct - 1.96*se_correct,
               label = round(mean_correct, 2))) +
    geom_pointrange() +
    facet_wrap(~`Name type`) +
    labs(#title = glue("Between group assessment: 
         #A non-white assesses whites' names"),
         x = "Respondent", y = "% correct") +
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    ylim(c(0.3 , 1)) 
```

```{r eval = FALSE}
################# FIGURE 3 #################
fig3 <- group_group_plot /
white_other_plot /
other_white_plot +patchwork::plot_annotation(tag_level = "A")

fig3

ggsave(here("plots", "res_race_identity_correspondence.jpg"), 
       width = 7,
       height = 8)

# for publication
ggsave(here("plots", "figure3.eps"), 
       width = 8,
       height = 10,
       device = "eps")

group_group_avg <- c(0.85, 0.77, 0.9, 0.89, 0.85, 0.77, 0.9, 0.89)

white_other_avg <- c(0.62, 0.64, 0.77, 0.63, 0.64, 0.77)

other_white_avg <- c(0.84, 0.61, 0.79, 0.84, 0.61, 0.79)

mean(group_group_avg) ; mean(c(white_other_avg, other_white_avg))

mean(white_other_avg) ; mean(other_white_avg)
```

## Dataset based on correspondence validation

Group -> Group 

Criterion: mean correct score 

Black: 8%
White: 2%
Asian: 18%
Latino: 11%

```{r}
high_quality_group_group_names <- map2_dfr(c("Black", "White", "AAPI", "Latino"), c("Black", "White", "AAPI", "Latino"), better_than_mean_names)

high_quality_group_group_names %>%
    select(res.race, identity, pct_quality_names) %>%
    distinct()

# CSV
write_csv(high_quality_group_group_names, here("data_outputs", "hq_group_group_names.csv"))

# RDS
write_rds(high_quality_group_group_names, here("data_outputs", "hq_group_group_names.rds"))
```

White -> Minority 

Criterion: identical 

White -> Black: 2%
White -> Asian: 2%
White -> Latino: 1%

```{r}
high_quality_white_other_names <- map2_dfr(rep("White", 3),  c("Black", "AAPI", "Latino"), better_than_mean_names)

high_quality_white_other_names %>%
    select(res.race, identity, pct_quality_names) %>%
    distinct()

# CSV
write_csv(high_quality_white_other_names, here("data_outputs", "hq_white_other_names.csv"))

# RDS
write_rds(high_quality_white_other_names, here("data_outputs", "hq_white_other_names.rds"))
```

Minority -> White 

Criterion: identical 

Black -> White: 8%
Asian -> White: 18%
Latino -> White: 11%

```{r}
high_quality_other_white_names <- map2_dfr(c("Black", "AAPI", "Latino"), rep("White", 3), better_than_mean_names)

high_quality_other_white_names %>%
    select(res.race, identity, pct_quality_names) %>%
    distinct()

# CSV
write_csv(high_quality_other_white_names, here("data_outputs", "hq_other_white_names.csv"))

# RDS
write_rds(high_quality_other_white_names, here("data_outputs", "hq_other_white_names.rds"))
```

# Information equivalence

## Visualization 

```{r}
study123$income.ord <- normalize(study123$income.ord)
study123$education.ord <- normalize(study123$education.ord)
```

```{r}
# identity values = "Black or African American," "White," "Asian or Pacific Islander," "Hispanic"

summ123 <- study123 %>%
    group_by(identity, w.asian, name) %>%
    summarize(Correct = mean(correct),
              Citizen = mean(citizen),
              Education = mean(education.ord, na.rm = T),
              Income = mean(income.ord, na.rm = T))

mod_black <- lm_robust(Correct ~ Citizen + Education + Income, data = subset(summ123, w.asian == 0 & identity == "Black or African American")) %>% 
    tidy() %>%
    mutate(identity = "Black")

mod_white <- lm_robust(Correct ~ Citizen + Education + Income, data = subset(summ123, w.asian == 0 & identity == "White")) %>% 
    tidy() %>%
    mutate(identity = "White")

mod_asian <- lm_robust(Correct ~ Citizen + Education + Income, data = subset(summ123, w.asian == 0 & identity == "Asian or Pacific Islander")) %>% 
    tidy() %>%
    mutate(identity = "Asian")

mod_wasian <- lm_robust(Correct ~ Citizen + Education + Income, data = subset(summ123, w.asian == 1 & identity == "Asian or Pacific Islander")) %>%
    tidy() %>%
    mutate(identity = "Asian (White first name)")

mod_latino <- lm_robust(Correct ~ Citizen + Education + Income, data = subset(summ123, w.asian == 0 & identity == "Hispanic")) %>% 
    tidy() %>%
    mutate(identity = "Latino")

all_mod <- bind_rows(mod_asian, mod_black, mod_latino, mod_wasian, mod_white)

all_mod %>%
    filter(!str_detect(term, "Inter")) %>%
    ggplot(aes(x = term, 
               y = estimate, 
               ymax = conf.high,
               ymin = conf.low,
               label = round(estimate, 2))) +
    geom_pointrange() +
    coord_flip() +
    geom_hline(yintercept = 0, linetype = "dashed") +
    labs(x = "", y = "Estimate") +
    facet_wrap(~identity) +
    geom_text_repel()

ggsave(here("plots", "estimate_by_race.jpg"))
```

## Dataset based on informaiton equivalence validation

```{r}
diff_res <- reduce(list(diff_summ("citizen", "citizen"),
                   diff_summ("education.ord", "education"),
                   diff_summ("income.ord", "income")),
                   full_join)

pct_correct_df <- study123 %>%
    ungroup() %>%
    select(identity, w.asian, name, correct) %>%
    group_by(identity, w.asian, name) %>%
    summarize(pct_correct = mean(correct))

diff_pct_correct <- left_join(diff_res, pct_correct_df)

# CSV
write_csv(diff_pct_correct, here("data_outputs", "pct_correct_covariate.csv"))

# RDS
write_rds(diff_pct_correct, here("data_outputs", "pct_correct_covariate.rds"))
```
